 

### 2020-12-04 doc/manuscript/tables_figures/tables.Rmd
update hypothesis table
https://github.com/EcoClimLab/growth_phenology/commit/571dd68a58006b25a32cc256c3e5673dc4243d12#commitcomment-44814447

#add footnote: 
kableExtra::footnote(number = c("One of nine species analyzed had significant positive response to April $T_{max}$; one had significant negative response to March $T_{max}$", "One of two species analyzed had signficant positive response to April $T_{max}$, both had negative response to May $T_{max}$", "The one species analyzed had a signficant negative response to April $T_{max}$."), footnote_as_chunk = FALSE, threeparttable=TRUE, escape = FALSE)
```

>>>>

#add footnote: 
kableExtra::footnote(number = c("One of nine species analyzed had significant positive response to April $T_{max}$; one had significant negative response to March $T_{max}$", "One of two species analyzed had signficant positive response to April $T_{max}$, both had negative response to May $T_{max}$", "One of the two species was negatively correlated with April $T_{max}$, and the other positively correlated with May $T_{max}$."), footnote_as_chunk = FALSE, threeparttable=TRUE, escape = FALSE)
```
